---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Simulated Survey Of Megafauna At Offshore Windfarms :airplane::dolphin:

<!-- badges: start -->
<!-- badges: end -->

<br/>

**sismow** was developed as part of the **OWFSOMM** project. The objective of this project is to demonstrate the technical relevance of aerial digital monitoring while ensuring their comparability with observer-based visual monitoring.

The goal of `sismow` is to simulate different **datasets of aerial monitoring**. To do this, `sismow` allows to simulate:

1. density maps
2. sampling transects
3. observation probabilities

With the different functions of this package, it is possible to simulate digital and visual aerial monitoring for different conditions (more or less abundant species, more or less homogeneously distributed in space, more or less discreet...). This allows then to calculate abundances and distributions under different conditions and to calculate intercalibration parameters between the two methods.

### Installation

---

You can install the development version of `sismow` from [GitHub](https://github.com/) with:

```{r}
# install.packages("devtools")
#devtools::install_github("maudqueroue/sismow")
library(sismow)
```

### Population Abundance Emulator

---

#### Simulate density

First, the function `simulate_density` allows to create map with different spatial variation of density.

##### Examples :
         
- **homogeneous**: same density througout the studied area.  

```{r, echo = FALSE, warning = FALSE, message = FALSE}
set.seed(2022)
library(ggplot2)

data("shape_courseulles")
shape_courseulles <- shape_courseulles %>%
    sf::st_transform(crs = 2154)
  
```
```{r, echo = TRUE, warning = FALSE}
map <- simulate_density(shape_obj = shape_courseulles,
                        density_type = "uniform")
```
```{r, echo = FALSE, warning = FALSE, fig.height = 3, fig.width= 7}
# Plot
ggplot() +
  geom_sf(data = map, aes(fill = density)) +
  theme(legend.position = "none",
        panel.background = element_rect(fill = "white"),
        panel.grid.major = element_line(colour = "#EDEDE9"),
        axis.title = element_text(size=5),
        axis.text = element_text(size=7),
        plot.title = element_text(size = 10, face = "bold")) +
  ggtitle("Homogeneous density")
```

- **gradient** : density decreasing from a hotspot that could be placed on different directions (`gradient_direction` : Center, North, East...). The `amplitude` and `wavelength` of the hotspot created can be modulated by the user.

```{r, echo = TRUE, warning = FALSE}
map <- simulate_density(shape_obj = shape_courseulles,
                        density_type = "gradient",
                        gradient_direction = "NW",
                        amplitude = 200,
                        wavelength = 40000)
```
```{r, echo = FALSE, warning = FALSE, fig.height = 3, fig.width= 7}
# Plot
ggplot() +
  geom_sf(data = map, aes(fill = density)) +
  theme(panel.background = element_rect(fill = "white"),
        panel.grid.major = element_line(colour = "#EDEDE9"),
        axis.title = element_text(size=5),
        axis.text = element_text(size=7),
        plot.title = element_text(size = 10, face = "bold")) +
  ggtitle("Gradient density")
```

- **Random**: random density. Several hotspots `nb_hotspots` are randomly created with amplitude and wavelength randomly chosen. The maximum value of `amplitude` and `wavelength` can be modulated by the user.
```{r, echo = TRUE, warning = FALSE}
map <- simulate_density(shape_obj = shape_courseulles,
                        density_type = "random",
                        amplitude = 200,
                        wavelength = 10000,
                        nb_hotspots = 15)
```
```{r, echo = FALSE, warning = FALSE, fig.height = 3, fig.width= 7}
# Plot
ggplot() +
  geom_sf(data = map, aes(fill = density)) +
  theme(panel.background = element_rect(fill = "white"),
        panel.grid.major = element_line(colour = "#EDEDE9"),
        axis.title = element_text(size=5),
        axis.text = element_text(size=7),
        plot.title = element_text(size = 10, face = "bold")) +
  ggtitle("Random density")
```

#### Simulate individuals
The `simulate_ind` function allows to simulate an approximate number of individuals/groups with an inhomogenous Poisson point process according to the densities provided in the `map` object.

##### Examples :    
- Simulation of `N` = 200 individuals with `mean_group_size` = 1:
```{r, echo = FALSE, warning = FALSE}
map <- simulate_density(shape_obj = shape_courseulles,
                        density_type = "gradient",
                        gradient_direction = "NW",
                        amplitude = 200,
                        wavelength = 40000)
```
```{r, echo = TRUE, warning = FALSE, message = FALSE}
ind <- simulate_ind(map_obj = map, 
                    mean_group_size = 1, 
                    N = 200)
```
```{r, echo = FALSE, warning = FALSE, fig.height = 3, fig.width= 7}
ggplot() +
  geom_sf(data = map, aes(fill = density)) +
  geom_point(data = ind, aes(x = x, y = y)) +
  theme(panel.background = element_rect(fill = "white"),
        panel.grid.major = element_line(colour = "#EDEDE9"),
        axis.title = element_text(size=5),
        axis.text = element_text(size=7),
        plot.title = element_text(size = 10, face = "bold")) +
  xlab("") +
  ylab("") +
  ggtitle("Simulated individuals")
```

- Simulation of `N` = 100 groups of `mean_group_size` 5 individuals
```{r, echo = TRUE, warning = FALSE}
ind <- simulate_ind(map_obj = map, 
                    mean_group_size = 5, 
                    N = 100)
```
```{r, echo = FALSE, warning = FALSE, fig.height = 3, fig.width= 7}
ggplot()+
  geom_sf(data = map, colour = "#EDEDE9") +
  geom_point(data = ind, aes(x = x, y = y, color = size)) +
  theme(panel.background = element_rect(fill = "white"),
        panel.grid.major = element_line(colour = "#EDEDE9"),
        axis.title = element_text(size=5),
        axis.text = element_text(size=7),
        plot.title = element_text(size = 10, face = "bold")) +
  xlab("") +
  ylab("") +
  ggtitle("Simulated groups")
```

### Sampling Design Emulator

---

#### Simulate transects
The function `simulate_transects` allows to simulate transects with different conditions:       
- different types of **survey design** such as parallel, zigzag, crossed zigzag or random transects       
- **total transect length** (approximately)   
- **angle** of the transects      
- **segmentation** of the transects
- **segments** length (approximately)

##### Examples:
- **parallel** transects design with an approximate total line length of **400km**:

```{r, warning = FALSE}
transects <- simulate_transects(shape_obj = shape_courseulles,
                             design = "systematic",
                             line_length = 400000)
```
```{r, echo = FALSE, warning = FALSE, fig.height = 3, fig.width= 7}
# Plot
ggplot() +
      geom_sf(data = shape_courseulles, fill = "#EDEDE9") +
      geom_sf(data = transects) +
      theme(panel.background = element_rect(fill = "white"),
      panel.grid.major = element_line(colour = "#EDEDE9"),
      axis.title = element_text(size=5),
      axis.text = element_text(size=7),
      plot.title = element_text(size = 10, face = "bold")) +
  ggtitle("Parallel design")
```

- **zigzag** transects design with an approximate total line length of **600km** that are segmentized with a `length of approximatively **2000m** per segment. 
```{r, warning = FALSE}
transects <- simulate_transects(shape_obj = shape_courseulles,
                             design = "eszigzag",
                             line_length = 600000,
                             design_angle = 90,
                             segmentize = TRUE,
                             seg_length = 2000)
```
```{r, echo = FALSE, warning = FALSE, fig.height = 3, fig.width= 7}
pal <- rep(c("#98C1D9","#EE6C4D","#293241"),nrow(transects)) 
ggplot() +
  geom_sf(data = shape_courseulles, fill = "#EDEDE9") +
  geom_sf(data = transects, aes(colour = seg_ID))+
  scale_colour_manual(values=pal) +
  theme(legend.position = "none",
        axis.title = element_text(size=5),
        axis.text = element_text(size=7),
        panel.background = element_rect(fill = "white"),
        panel.grid.major = element_line(colour = "#EDEDE9"),
        plot.title = element_text(size = 10, face = "bold")) +
  ggtitle("Zigzag design")
```

### Observation Data Emulator

---

#### Simulate observations 
The function `simulate_obs` allows to simulate datasets of observations according to:  

1. The **individuals/groups** simulated on the **density** map.   
2. The **transect design** simulated.   
3. A **detection probability**.        

To determine the detection probability, the user can choose:   
- The form of the detection function : **uniform** or **half-normal**   
- The maximum distance of observation (**truncation**)   
- The probability of observation at distance 0 (**g_zero**)   
- The effective strip width (**esw**) for half-normal detection function   

##### Examples:
- **Half normal** detection probability equal to **1** at 0 distance with a effective strip half width of **180m**. 
```{r, echo = FALSE, warning = FALSE}
# Then simulate the presence of individuals in the study area 
ind <- simulate_ind(map_obj = map, N = 500)

# Then create transects
transects <- simulate_transects(shape_obj = map,
                                design = "systematic",
                                line_length = 400000,
                                design_angle = 2,
                                segmentize = TRUE,
                                seg_length = 2000)
```
```{r, echo = TRUE, warning = FALSE}
obs <- simulate_obs(ind_obj = ind,
                    transect_obj = transects,
                    key = "hn",
                    g_zero = 1,
                    esw = 180)
```
```{r, echo = FALSE, warning = FALSE, fig.height = 3, fig.width= 7}
# Plot detection probability
ggplot(obs, aes(x=distance, y=proba)) +
  geom_point(color = "#EE6C4D") +
  xlim(0,500) +
  xlab("Distance")+
  ylab("Detection Probability") +
  theme(plot.title = element_text(size = 10, face = "bold"),
        axis.title = element_text(size=7),
        axis.text = element_text(size=7),) +
  ggtitle("Half Normal Detection Probability")

# Plot on map
ggplot() +
  geom_sf(data = map, fill = "#CDDAFD", color = "#CDDAFD") +
  geom_sf(data = transects, color = "black") +
  geom_point(data=obs[obs$detected==0,], aes(x=x, y=y), shape=20, color="#051923") +
  geom_point(data=obs[obs$detected==1,], aes(x=x, y=y), shape=21, fill="#EE6C4D") +
  labs(caption = paste("Sightings = ", sum(obs$detected), sep = " ")) +
  theme(legend.position = "none",
        panel.background = element_rect(fill = "white"),
        panel.grid.major = element_line(colour = "#EDEDE9"),
        axis.title = element_text(size=5),
        axis.text = element_text(size=7),
        plot.title = element_text(size = 10, face = "bold")) +
  xlab("")+
  ylab("") +
  ggtitle("Half Normal Detection Probability")

```
- **Uniform** detection probability equal to **1** below distance **200m** .  
```{r, echo = TRUE, warning = FALSE}
obs <- simulate_obs(ind_obj = ind,
                    transect_obj = transects,
                    key = "unif",
                    g_zero = 1,
                    truncation = 200)
```
```{r, echo = FALSE, warning = FALSE, fig.height = 3, fig.width= 7}
# Plot detection probability
ggplot(obs, aes(x=distance, y=proba)) +
  geom_point(color = "#EE6C4D") +
  xlim(0,500) +
  xlab("Distance")+
  ylab("Detection Probability") +
  theme(plot.title = element_text(size = 10, face = "bold"),
        axis.title = element_text(size=7),
        axis.text = element_text(size=7),) +
  ggtitle("Uniform Detection Probability") 

# Plot on map
ggplot() +
  geom_sf(data = map, fill = "#CDDAFD", color = "#CDDAFD") +
  geom_sf(data = transects, color = "black") +
  geom_point(data=obs[obs$detected==0,], aes(x=x, y=y), shape=20, color="#051923") +
  geom_point(data=obs[obs$detected==1,], aes(x=x, y=y), shape=21, fill="#EE6C4D") +
  labs(caption = paste("Sightings = ", sum(obs$detected), sep = " ")) +
  theme(legend.position = "none",
        panel.background = element_rect(fill = "white"),
        axis.title = element_text(size=3),
        axis.text = element_text(size=7),
        panel.grid.major = element_line(colour = "#EDEDE9"),
        plot.title = element_text(size = 10, face = "bold")) +
  xlab("")+
  ylab("") +
  ggtitle("Uniform Detection Probability")



```

