---
title: "flat_sampling_design_emulator.Rmd empty"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r development, include=FALSE}
library(testthat)
```

## Simulate Transects
`simulate_transects` allows to simulate transects with different conditions :     

- different types of **survey design** such as parallel, zigzag, crossed zigzag or random transects       
- **total transect length** (approximately)   
- **angle** of the transects      
- **segmentation** of the transects
- **segment** length (approximately)

The output is a sf dataframe containing the simulated transects. The dataframe contains four columns:         
- `transect` : number of the transect    
- `seg_ID` : a unique identifiant for each segments/transect    
- `effort` : length of each segment/transect    
- `geometry` : geometry of the transects    

```{r function-simulate_transects}

#' Simulate Transects
#'
#' @description
#' `simulate_transects` allows to simulate transects with different designs and total length. It also allows to segmentize the simulated transects.
#
#' @details
#' This function use create the `make.design` function of the `dssd` package.
#'
#' If segmentize is `TRUE`, `seg_ID` is noted "1-2" for transect 1 segment 2. If segmentize is `FALSE`, `seg_ID` is identical to the transect number (first column).
#'
#' @param shape_obj sf object. The shape of the study site or a density grid.
#' @param design character. Variable describing the type of design. Either `random`, `systematic` (parallel), `eszigzag` (equal-spaced zigzag), `eszigzagcom` (equal spaced crossed zigzag). See `dssd` package for more information.
#' @param design_angle numeric. Value detailing the angle of the design. A value of -1 will cause a random design angle to be generated. See `dssd` package for more information. By default: 0.
#' @param line_length numeric. The approximative total line length desired in m.
#' @param segmentize boolean. If `TRUE` transects are segmented and a `seg_ID` is given to each segment. If `FALSE`transects are not segmented. By default: `FALSE`.
#' @param seg_length numeric. Length of the segments desired for segmentation.
#' @param crs numeric. Projection system. By default: 2154.
#' @param ... All other arguments that could be used in the make.design function. See dssd package for more information.
#'
#' @importFrom dssd make.design generate.transects
#' @importFrom sf st_cast st_sf st_geometry st_multilinestring st_sfc st_coordinates st_set_geometry st_crs st_geometry_type st_segmentize st_length st_union st_intersection
#' @importFrom dplyr select mutate
#' @importFrom assertthat assert_that
#' @importFrom units set_units
#'
#' @return The simulated transects corresponding to the differents conditions in a sf dataframe. The dataframe contains four columns: `transect` number, `seg_ID` (a unique identifiant for each segments/transect), `effort` (length of each segment/transect) and `geometry`.
#' @export

simulate_transects <- function(shape_obj, design = "systematic", design_angle = 0, line_length, segmentize = FALSE, seg_length, crs = 2154, ...) {
  
  # Function checks
  assert_that(inherits(shape_obj, "sf"))
  assert_that(is.numeric(crs))
  assert_that(is.numeric(line_length))
  assert_that(is.numeric(design_angle))
    if(!(design %in% c("random","systematic","eszigzag","eszigzagcom"))){stop("Design argument must be 'random', 'systematic', 'eszigzag' or 'eszigzagcom'.")}


  # Function
  shape_obj <- shape_obj %>%
    st_transform(crs = crs) %>%
    st_union()
  
  
  region_obj <- make.region(region.name = "Study site",
                            shape = shape_obj,
                            units = "m")
  
  transect.design <- make.design(region = region_obj,
                                 design = design,
                                 design.angle = design_angle,
                                 line.length = line_length,
                                 ...)
  
  transect.survey <- generate.transects(transect.design)
  
  x <- transect.survey@samplers %>%
    as.data.frame() %>%
    select("transect","geometry") %>%
    st_sf(crs = crs) #%>%
    #st_cast("LINESTRING")
  
if(segmentize == TRUE){
  
  ### Segmentize
  #-----------------
  assert_that(is.numeric(seg_length))
  
  transect_obj <- st_segmentize(x, dfMaxLength = set_units(seg_length, "metres"))
  # geometry
  ggg <- st_geometry(transect_obj)
  
  # check
  if (isFALSE(st_geometry_type(ggg) %in% c("LINESTRING"))) {
    stop("Input should be LINESTRING")
  }
  
  # loop to segmentize
  for (k in 1:length(st_geometry(ggg))) {
    # segment in each transect as sf multilinestring
    sub <- ggg[k]
    geom <- lapply(1:(length(st_coordinates(sub)[, 1]) - 1),
      function(i)rbind(as.numeric(st_coordinates(sub)[i, 1:2]), as.numeric(st_coordinates(sub)[i + 1, 1:2]))) %>%
      st_multilinestring() %>%
      st_sfc()
    # create endgeom with the multilinestring for each transect
    if (k == 1) {endgeom <- geom}
    else {endgeom <- rbind(endgeom, geom)}
  }
  
  # sf object
  endgeom <- endgeom %>% 
    st_sfc(crs = crs) 

  # Multilinestring to linestring
  endgeom <- st_set_geometry(transect_obj, endgeom) %>% 
    st_cast("LINESTRING") 
  
  ### Add effort
  #----------------
  endgeom$effort <- st_length(endgeom)
  
  ### Name segment
  #-----------------
  endgeom$seg_ID <- NA
  # loop over the transect IDs
  for(this_transect in unique(endgeom$transect)){
    # how many segments in this transect?
    n_segs <- nrow(subset(endgeom, transect==this_transect))
    # generate the n_segs labels that we need
    endgeom$seg_ID[endgeom$transect==this_transect] <- paste(this_transect, 1:n_segs, sep="-")}
  
  x <- endgeom
  }
  
  if(segmentize == FALSE){
    x <- x %>% 
      mutate(seg_ID = transect) %>%
      mutate(effort = st_length(.))
  }
  
  x <- x %>%
    st_intersection(shape_obj) %>%
    select(transect, seg_ID, effort, geometry)
  
  return(x)
}

```

### Examples

For these examples, `shape_courseulles`, a dataframe included in this package is used. With `simulate_transects` some transect designs are simulated:     
- (1) **parallel** transects with an approximate total line length of **400km**    
- (2) **zigzag** transects with an approximate line length of **400km** that are segmented with a length of approximatively **2000m** per segment.    
- (3) the `shape_obj` is a density map simulated with `simulate_density` and the design is **parallel** transects with an approximate total line length of **400km** that are segmented with a length of approximatively **2000m** per segments.

```{r examples-simulate_transects, warning = FALSE, fig.height = 3, fig.width= 7}

library(ggplot2)
data("shape_courseulles")

# ------------------------------
# Example 1 : parallel transects with an approximate total line length of 400000m
# ------------------------------

transects <- simulate_transects(shape_obj = shape_courseulles,
                             design = "systematic",
                             line_length = 400000)
# Plot
ggplot() +
      geom_sf(data = shape_courseulles, fill = "#EDEDE9") +
      geom_sf(data = transects) +
      theme(panel.background = element_rect(fill = "white"),
      panel.grid.major = element_line(colour = "#EDEDE9"))

# ------------------------------
# Example 2 : zigzag transects with an approximate total line length of 400000m 
# that are segmented with a length of approximately 2000m per segment
# ------------------------------

transects <- simulate_transects(shape_obj = shape_courseulles,
                             design = "eszigzag",
                             line_length = 400000,
                             design_angle = 90,
                             segmentize = TRUE,
                             seg_length = 2000)

# Plot
pal <- rep(c("#98C1D9","#EE6C4D","#293241"),nrow(transects)) 
ggplot() +
      geom_sf(data = shape_courseulles, fill = "#EDEDE9") +
      geom_sf(data = transects, aes(colour = seg_ID))+
      scale_colour_manual(values=pal) +
      theme(legend.position = "none",
      panel.background = element_rect(fill = "white"),
      panel.grid.major = element_line(colour = "#EDEDE9"))


# ------------------------------
# Example 3 : systematic parallel transects with an approximative total length of 400000m
# that are segmented with a length of approximately 2000m per segment 
# the `shape_obj` is a density map simulated with `simulate_density`
#-------------------------------

# Create map 
map <- simulate_density(shape_obj = shape_courseulles,
                              grid_size = 1000,
                              density_type = "gradient",
                              gradient_direction = "N",
                              wavelength = 20000,
                              amplitude = 500)

# Create transects
transects <- simulate_transects(shape_obj = map,
                             design = "systematic",
                             line_length = 400000,
                             design_angle = 2,
                             segmentize = TRUE,
                             seg_length = 2000)

# Plot
pal <- rep(c("#98C1D9","#EE6C4D","#293241"),nrow(transects)) 
ggplot() +
      geom_sf(data = map, color = "#D9D9D9") +
      geom_sf(data = transects, aes(colour = seg_ID))+
      scale_colour_manual(values = pal) +
      theme(legend.position = "none",
      panel.background = element_rect(fill = "white"),
      panel.grid.major = element_line(colour = "#EDEDE9"))

```

```{r tests-simulate_transects}
library(testthat)
library(dplyr)

test_that("simulate_transects works", {
  expect_true(inherits(simulate_transects, "function"))
})

test_that("test conformite simulate_transects", {

  data("shape_courseulles")
  
  set.seed(2022)
  
  map <- simulate_density(shape_obj = shape_courseulles,
                              grid_size = 1000,
                              density_type = "gradient",
                              gradient_direction = "N",
                              wavelength = 20000,
                              amplitude = 500)
  

  test_1 <- simulate_transects(shape_obj = shape_courseulles,
                             design = "systematic",
                             line_length = 400000,
                             design_angle = 2) %>%
    slice(1:5)
  
  test_2 <- simulate_transects(shape_obj = map,
                             design = "systematic",
                             line_length = 400000,
                             design_angle = 2,
                             segmentize = TRUE,
                             seg_length = 2000) %>%
    slice(1:5)

  exp_1 <- structure(list(transect = 1:5, seg_ID = 1:5, effort = structure(c(18772.895468405, 
28654.059654105, 25288.2990032283, 27027.8662220783, 29795.8965123036
), units = structure(list(numerator = "m", denominator = character(0)), class = "symbolic_units"), class = "units"), 
    geometry = structure(list(structure(c(394055.793731328, 394710.958334824, 
    6936392.0721311, 6955153.53165881), dim = c(2L, 2L), class = c("XY", 
    "LINESTRING", "sfg")), structure(c(401360.757117791, 402360.769378203, 
    6926116.13476568, 6954752.73914085), dim = c(2L, 2L), class = c("XY", 
    "LINESTRING", "sfg")), structure(c(409128.031513907, 410010.580421582, 
    6929079.05256815, 6954351.9466229), dim = c(2L, 2L), class = c("XY", 
    "LINESTRING", "sfg")), structure(c(416717.132536868, 417660.391464961, 
    6926939.75252869, 6953951.15410494), dim = c(2L, 2L), class = c("XY", 
    "LINESTRING", "sfg")), structure(c(424270.340716261, 425310.20250834, 
    6923772.61592977, 6953550.36158698), dim = c(2L, 2L), class = c("XY", 
    "LINESTRING", "sfg"))), class = c("sfc_LINESTRING", "sfc"
    ), precision = 0, bbox = structure(c(xmin = 394055.793731328, 
    ymin = 6923772.61592977, xmax = 425310.20250834, ymax = 6955153.53165881
    ), class = "bbox"), crs = structure(list(input = "EPSG:2154", 
        wkt = "PROJCRS[\"RGF93 / Lambert-93\",\n    BASEGEOGCRS[\"RGF93\",\n        DATUM[\"Reseau Geodesique Francais 1993\",\n            ELLIPSOID[\"GRS 1980\",6378137,298.257222101,\n                LENGTHUNIT[\"metre\",1]]],\n        PRIMEM[\"Greenwich\",0,\n            ANGLEUNIT[\"degree\",0.0174532925199433]],\n        ID[\"EPSG\",4171]],\n    CONVERSION[\"Lambert-93\",\n        METHOD[\"Lambert Conic Conformal (2SP)\",\n            ID[\"EPSG\",9802]],\n        PARAMETER[\"Latitude of false origin\",46.5,\n            ANGLEUNIT[\"degree\",0.0174532925199433],\n            ID[\"EPSG\",8821]],\n        PARAMETER[\"Longitude of false origin\",3,\n            ANGLEUNIT[\"degree\",0.0174532925199433],\n            ID[\"EPSG\",8822]],\n        PARAMETER[\"Latitude of 1st standard parallel\",49,\n            ANGLEUNIT[\"degree\",0.0174532925199433],\n            ID[\"EPSG\",8823]],\n        PARAMETER[\"Latitude of 2nd standard parallel\",44,\n            ANGLEUNIT[\"degree\",0.0174532925199433],\n            ID[\"EPSG\",8824]],\n        PARAMETER[\"Easting at false origin\",700000,\n            LENGTHUNIT[\"metre\",1],\n            ID[\"EPSG\",8826]],\n        PARAMETER[\"Northing at false origin\",6600000,\n            LENGTHUNIT[\"metre\",1],\n            ID[\"EPSG\",8827]]],\n    CS[Cartesian,2],\n        AXIS[\"easting (X)\",east,\n            ORDER[1],\n            LENGTHUNIT[\"metre\",1]],\n        AXIS[\"northing (Y)\",north,\n            ORDER[2],\n            LENGTHUNIT[\"metre\",1]],\n    USAGE[\n        SCOPE[\"Engineering survey, topographic mapping.\"],\n        AREA[\"France - onshore and offshore, mainland and Corsica.\"],\n        BBOX[41.15,-9.86,51.56,10.38]],\n    ID[\"EPSG\",2154]]"), class = "crs"), n_empty = 0L)), row.names = c(NA, 
-5L), class = c("sf", "data.frame"), sf_column = "geometry", agr = structure(c(transect = NA_integer_, 
seg_ID = NA_integer_, effort = NA_integer_), class = "factor", levels = c("constant", 
"aggregate", "identity")))
  
  
  exp_2 <- structure(list(transect = c(1L, 1L, 1L, 1L, 1L), seg_ID = c("1-1", 
"1-2", "1-3", "1-4", "1-5"), effort = structure(c(1876.14289556029, 
1876.14289556029, 1876.14289556029, 1876.14289556029, 1876.14289556122
), units = structure(list(numerator = "m", denominator = character(0)), class = "symbolic_units"), class = "units"), 
    geometry = structure(list(structure(c(393461.469060267, 393526.945503064, 
    6938158.74575047, 6940033.74575047), dim = c(2L, 2L), class = c("XY", 
    "LINESTRING", "sfg")), structure(c(393526.945503064, 393592.421945861, 
    6940033.74575047, 6941908.74575047), dim = c(2L, 2L), class = c("XY", 
    "LINESTRING", "sfg")), structure(c(393592.421945861, 393657.898388658, 
    6941908.74575047, 6943783.74575047), dim = c(2L, 2L), class = c("XY", 
    "LINESTRING", "sfg")), structure(c(393657.898388658, 393723.374831455, 
    6943783.74575047, 6945658.74575047), dim = c(2L, 2L), class = c("XY", 
    "LINESTRING", "sfg")), structure(c(393723.374831455, 393788.851274252, 
    6945658.74575047, 6947533.74575047), dim = c(2L, 2L), class = c("XY", 
    "LINESTRING", "sfg"))), class = c("sfc_LINESTRING", "sfc"
    ), precision = 0, bbox = structure(c(xmin = 393461.469060267, 
    ymin = 6938158.74575047, xmax = 393788.851274252, ymax = 6947533.74575047
    ), class = "bbox"), crs = structure(list(input = "EPSG:2154", 
        wkt = "PROJCRS[\"RGF93 / Lambert-93\",\n    BASEGEOGCRS[\"RGF93\",\n        DATUM[\"Reseau Geodesique Francais 1993\",\n            ELLIPSOID[\"GRS 1980\",6378137,298.257222101,\n                LENGTHUNIT[\"metre\",1]]],\n        PRIMEM[\"Greenwich\",0,\n            ANGLEUNIT[\"degree\",0.0174532925199433]],\n        ID[\"EPSG\",4171]],\n    CONVERSION[\"Lambert-93\",\n        METHOD[\"Lambert Conic Conformal (2SP)\",\n            ID[\"EPSG\",9802]],\n        PARAMETER[\"Latitude of false origin\",46.5,\n            ANGLEUNIT[\"degree\",0.0174532925199433],\n            ID[\"EPSG\",8821]],\n        PARAMETER[\"Longitude of false origin\",3,\n            ANGLEUNIT[\"degree\",0.0174532925199433],\n            ID[\"EPSG\",8822]],\n        PARAMETER[\"Latitude of 1st standard parallel\",49,\n            ANGLEUNIT[\"degree\",0.0174532925199433],\n            ID[\"EPSG\",8823]],\n        PARAMETER[\"Latitude of 2nd standard parallel\",44,\n            ANGLEUNIT[\"degree\",0.0174532925199433],\n            ID[\"EPSG\",8824]],\n        PARAMETER[\"Easting at false origin\",700000,\n            LENGTHUNIT[\"metre\",1],\n            ID[\"EPSG\",8826]],\n        PARAMETER[\"Northing at false origin\",6600000,\n            LENGTHUNIT[\"metre\",1],\n            ID[\"EPSG\",8827]]],\n    CS[Cartesian,2],\n        AXIS[\"easting (X)\",east,\n            ORDER[1],\n            LENGTHUNIT[\"metre\",1]],\n        AXIS[\"northing (Y)\",north,\n            ORDER[2],\n            LENGTHUNIT[\"metre\",1]],\n    USAGE[\n        SCOPE[\"Engineering survey, topographic mapping.\"],\n        AREA[\"France - onshore and offshore, mainland and Corsica.\"],\n        BBOX[41.15,-9.86,51.56,10.38]],\n    ID[\"EPSG\",2154]]"), class = "crs"), n_empty = 0L)), row.names = c("1", 
"1.1", "1.2", "1.3", "1.4"), class = c("sf", "data.frame"), sf_column = "geometry", agr = structure(c(transect = NA_integer_, 
seg_ID = NA_integer_, effort = NA_integer_), class = "factor", levels = c("constant", 
"aggregate", "identity")))

expect_equal(object = test_1,
             expected = exp_1)

expect_equal(object = test_2,
             expected = exp_2)

expect_is(test_1, "data.frame")
expect_is(test_2, "data.frame")

})

test_that("test erreur simulate_transects", {
  
  data(iris)
  
  expect_error(object = simulate_transects(shape_obj = map,
                                         design = "hoho",
                                         line_length = 400000,
                                         design_angle = 2,
                                         segmentize = TRUE,
                                         seg_length = 2000))
    
  expect_error(object = simulate_transects(shape_obj = iris,
                                         design = "systematic",
                                         line_length = 400000))
  
  expect_error(object = simulate_transects(shape_obj = map,
                                         design = "systematic",
                                         line_length = "nop"))
  
  expect_error(object = simulate_transects(shape_obj = map,
                                         design = "systematic",
                                         line_length = 400000,
                                         design_angle = "haha"))
  
  expect_error(object = simulate_transects(shape_obj = map,
                                         design = "systematic",
                                         line_length = 400000,
                                         design_angle = 0,
                                         segmentize = TRUE,
                                         seg_length = "hehe"))
})

```


```{r development-inflate, eval=FALSE}
# Run but keep eval=FALSE to avoid infinite loop
# Execute in the console directly
fusen::inflate(flat_file = "dev/flat_sampling_design_emulator.Rmd", 
               vignette_name = "Sampling Design Emulator",
               open_vignette = FALSE,
               check = FALSE,
               overwrite = TRUE)
```
