---
title: "flat_minimal.Rmd empty"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r development, include=FALSE}
library(testthat)
```

<!--
 You need to run the 'description' chunk in the '0-dev_history.Rmd' file before continuing your code there.
-->

## Simulate density maps

The `simulate_density`function allows to simulate different densities in a given area:         

- A **homogeneous** density with the same density througout the aera.    
- A **gradient** density with a density decreasing from a hotspot that could be placed on different direction: North, North-East, East, South-East, South, South-West, West, North-West and center). The amplitude and the wavelength of the hotspot created can be modified by the user.    
- A **random** density, created by adding a certain number of hotspots on the area. Each hotspot created have an amplitude and a wavelength randomly chosen between 1 and a maximum amplitude and a maximum wavelength that can be modified by the user.     

The output is a sf dataframe of the simulated density on the map. The dataframe contains two columns:    
- `density` : density simulated for each square of the grid    
- `geometry` : geometry of the grid 

```{r function-simulate_density}


#' Simulate density maps
#'
#' @description
#' `simulate_density` allows to simulate density with different spatial variation. 
#'
#' @details
#' This function use create the `make.density` and the `add.hotspot` functions of the `dsims` package.
#'
#' To simulate density on the map, a grid is created. The length of square side could be chosen by the user with `grid_size`. 
#'
#' If `density_type` is '`gradient`', one hotspot is added on one direction `gradient_direction` (North, North-East, East, South-East, South, South-West, West, North-West and center). The hotspot added have a `amplitude` and a `wavelength` chosen by the user. 
#'
#' If `density_type` is '`random`', several hotspots, the number is chosen by the user with the argument `nb_hotspots`, are added randomly in the area.The amplitude and wavelength of the differents hotspot are chosen randomly between a minimum of 1 and a maximum corresponding to the `amplitude` and `wavelength` chosen by the user. 
#'
#'
#' @param shape_obj sf object. The shape of the study site.
#' @param grid_size numeric. Length of length of square side. By default: 1000.
#' @param density_type character. 'uniform", 'gradient', 'random', 'covariate'.
#' @param gradient_direction character. Only for "gradient" `density_type`. Where the highest density comes from. 'N' for North,'NE','E'... and 'C" for center
#' @param wavelength numeric. Only for "gradient" and "random" `density_type`. Wavelength of the hotspots of density created. Maximum wavelength for "random" `density_type`. 
#' @param amplitude numeric. Only for "gradient" and "random" `density_type`. Amplitude of the hotspots of density created. Maximum amplitude for "random" `density_type`. 
#' @param nb_hotspots numeric. Only for "random" `density_type`. Number of random hotspots to be created.
#' @param crs numeric. Only for "random" `density_type`. Number of random hotspots to be created. By default: 2154.
#'
#' @importFrom sf st_area st_sfc st_contains as_Spatial st_point st_sf st_transform
#' @importFrom sp bbox
#' @importFrom dssd make.region
#' @importFrom dsims make.density add.hotspot
#' @importFrom dplyr mutate filter select
#' @importFrom units drop_units
#' @importFrom stats runif
#' @importFrom assertthat assert_that
#'
#' @return The map in a sf dataframe contaning the simulated density. The dataframe contains two columns, `density` simulated for each square of the grid and `geometry` of the grid. 
#' @export

simulate_density <- function(shape_obj, grid_size = 1000, density_type, gradient_direction, wavelength, amplitude, nb_hotspots, crs = 2154) {
  
  
  # function checks
  assert_that(inherits(shape_obj, "sf"))
  assert_that(is.numeric(grid_size))
  assert_that(is.numeric(crs))
  if(!(density_type %in% c("random","gradient","uniform"))){stop("Density_type argument must be 'random', 'gradient', or 'uniform'.")}

  # function
  shape_obj <- shape_obj %>%
    st_transform(crs = crs)
  
  xlim <- bbox(as_Spatial(shape_obj))[1, ]
  ylim <- bbox(as_Spatial(shape_obj))[2, ]
  
  
  region_obj <- make.region(region.name = "Study site",
                            shape = shape_obj,
                            units = "m")
  
  if(density_type == "uniform"){ 
    
    density_obj <- make.density(region = region_obj,
                                x.space = grid_size,
                                y.space = grid_size,
                                constant = 1)
    
  }
  
  
  if(density_type == "gradient"){
    
    assert_that(is.character(gradient_direction))
    if(!(gradient_direction %in% c("N", "NE","E","SE","S","SW","W","NW","C"))){stop("Gradient_direction argument must be 'N', 'NE', 'E', 'SE', 'S', 'SW', 'W', 'NW' or 'C'.")}
    assert_that(is.numeric(amplitude))
    assert_that(is.numeric(wavelength))

    
    if(gradient_direction == "N") {          
      x <- mean(xlim)  
      y <- max(ylim)
    }
    if(gradient_direction == "NE") {
      x <- max(xlim)  
      y <- max(ylim)
    }
    
    if(gradient_direction == "E"){
      x <- max(xlim) 
      y <- mean(ylim)
    }
    
    if(gradient_direction == "SE"){
      x <- max(xlim) 
      y <- min(ylim)
    }
    
    if(gradient_direction == "S") {
      x <- mean(xlim)  
      y <- min(ylim)
    }
    
    if(gradient_direction == "SW"){
      x <- min(xlim)  
      y <- min(ylim)
    }
    
    if(gradient_direction == "W"){
      x <- min(xlim)
      y <- mean(ylim) 
    }
    
    if(gradient_direction == "NW"){
      x <- min(xlim)
      y <- max(ylim)
    }
    
    if(gradient_direction == "C"){
      x <- mean(xlim)
      y <- mean(ylim)
    }
    
    density_obj <- make.density(region = region_obj,
                                x.space = grid_size,
                                y.space = grid_size,
                                constant = 1)
    
    density_obj <- add.hotspot(object = density_obj,
                               centre = c(x, y),
                               sigma = wavelength,
                               amplitude = amplitude)
    
  }
  

    if(density_type == "random"){

    assert_that(is.numeric(amplitude))
    assert_that(is.numeric(wavelength))
    assert_that(is.numeric(nb_hotspots))
    
      
          density_obj <- make.density(region = region_obj,
                                x.space = grid_size,
                                y.space = grid_size,
                                constant = 1)
          
          for(i in 1:nb_hotspots){
            
            sigma_n <- runif(1, 1, wavelength)
            amplitude_n <- runif(1, 1, amplitude)
            
            x <- runif(1, xlim[1], xlim[2])
            y <- runif(1, ylim[1], ylim[2])
            
            point <- st_sfc(st_point(c(x,y)), crs = crs)
            a <- as.numeric(st_contains(shape_obj, point))
            
            while(is.na(a==1)){
              
              x <- runif(1, xlim[1], xlim[2])
              y <- runif(1, ylim[1], ylim[2])
              
              point <- st_sfc(st_point(c(x,y)), crs = crs)
              
              a <- as.numeric(st_contains(shape_obj, point))
            }
            
            density_obj <- add.hotspot(object = density_obj,
                                       centre = c(x, y),
                                       sigma = sigma_n,
                                       amplitude = amplitude_n)
            
            rm(a, x, y, sigma_n, amplitude_n)
            
          }
    }
      

    
  # if(density_type == "covariate") {
  #   
  #   density_obj <- make.density(region = region_obj,
  #                               x.space = grid_size,
  #                               y.space = grid_size,
  #                               constant = 1)
  # }
  
  
  map_obj <- density_obj@density.surface %>%
    as.data.frame() %>%
    st_sf(crs = crs) %>%
    mutate(area = st_area(.)) %>%
    mutate(area_grid = grid_size^2) %>%
    drop_units() %>%
    filter(area == area_grid) %>%
    select(density, geometry)
  
}

```

### Examples

For these examples, `shape_courseulles`, a dataframe included in this package is used. With `simulate_density` some density maps are simulated:     
- (1) a **gradient** density map with a hotspot of density in the North     
- (2) a **random** density map with 10 random hotspots   

```{r examples-simulate_density, warning = FALSE,fig.height = 3, fig.width= 7}

library(ggplot2)
data("shape_courseulles")

# ------------------------------
# Example 1: Simulate a map with a gradient density from the North
#-------------------------------

map <- simulate_density(shape_obj = shape_courseulles,
                              density_type = "gradient",
                              gradient_direction = "N",
                              wavelength = 20000,
                              amplitude = 10)

# Plot
ggplot() +
  geom_sf(data = map, aes(fill = density)) +
  theme(panel.background = element_rect(fill = "white"),
        panel.grid.major = element_line(colour = "#EDEDE9"))


# ------------------------------
# Example 2: Simulate a map with a random density
# ------------------------------

map <- simulate_density(shape_obj = shape_courseulles,
                              density_type = "random",
                              wavelength = 10000,
                              amplitude = 15,
                              nb_hotspots = 10
                              
)

# Plot 
ggplot() +
  geom_sf(data = map, aes(fill = density)) +
  theme(panel.background = element_rect(fill = "white"),
        panel.grid.major = element_line(colour = "#EDEDE9"))

```

```{r tests-simulate_density}
library(testthat)
library(dplyr)


test_that("simulate_density works", {
  expect_true(inherits(simulate_density, "function")) 
})


test_that("test conformite simulate_density", {
  
  data("shape_courseulles")
  
  set.seed(2022)
  
  # First, create a density map
  test_1 <- simulate_density(shape_obj = shape_courseulles,
                            density_type = "gradient",
                            gradient_direction = "NW",
                            wavelength = 20000,
                            amplitude = 500) %>%
    slice(1:5)
  
  
  
  
  test_2 <- simulate_density(shape_obj = shape_courseulles,
                              density_type = "random",
                              wavelength = 10000,
                              amplitude = 15,
                              nb_hotspots = 10) %>%
    slice(1:5)
  
  
  test_3 <- simulate_density(shape_obj = shape_courseulles,
                             density_type = "uniform") %>%
    slice(1:5)
  
  
  exp_1 <- structure(list(density = c(1.06893079882588, 1.05714563936609, 
1.04725710843882, 1.03898212024591, 1.03207583958285), geometry = structure(list(
    structure(list(structure(c(462199.599999965, 462199.599999965, 
    463199.599999965, 463199.599999965, 462199.599999965, 6915158.74575047, 
    6916158.74575047, 6916158.74575047, 6915158.74575047, 6915158.74575047
    ), .Dim = c(5L, 2L))), class = c("XY", "POLYGON", "sfg")), 
    structure(list(structure(c(463199.599999965, 463199.599999965, 
    464199.599999965, 464199.599999965, 463199.599999965, 6915158.74575047, 
    6916158.74575047, 6916158.74575047, 6915158.74575047, 6915158.74575047
    ), .Dim = c(5L, 2L))), class = c("XY", "POLYGON", "sfg")), 
    structure(list(structure(c(464199.599999965, 464199.599999965, 
    465199.599999965, 465199.599999965, 464199.599999965, 6915158.74575047, 
    6916158.74575047, 6916158.74575047, 6915158.74575047, 6915158.74575047
    ), .Dim = c(5L, 2L))), class = c("XY", "POLYGON", "sfg")), 
    structure(list(structure(c(465199.599999965, 465199.599999965, 
    466199.599999965, 466199.599999965, 465199.599999965, 6915158.74575047, 
    6916158.74575047, 6916158.74575047, 6915158.74575047, 6915158.74575047
    ), .Dim = c(5L, 2L))), class = c("XY", "POLYGON", "sfg")), 
    structure(list(structure(c(466199.599999965, 466199.599999965, 
    467199.599999965, 467199.599999965, 466199.599999965, 6915158.74575047, 
    6916158.74575047, 6916158.74575047, 6915158.74575047, 6915158.74575047
    ), .Dim = c(5L, 2L))), class = c("XY", "POLYGON", "sfg"))), class = c("sfc_POLYGON", 
"sfc"), precision = 0, bbox = structure(c(xmin = 462199.599999965, 
ymin = 6915158.74575047, xmax = 467199.599999965, ymax = 6916158.74575047
), class = "bbox"), crs = structure(list(input = "EPSG:2154", 
    wkt = "PROJCRS[\"RGF93 / Lambert-93\",\n    BASEGEOGCRS[\"RGF93\",\n        DATUM[\"Reseau Geodesique Francais 1993\",\n            ELLIPSOID[\"GRS 1980\",6378137,298.257222101,\n                LENGTHUNIT[\"metre\",1]]],\n        PRIMEM[\"Greenwich\",0,\n            ANGLEUNIT[\"degree\",0.0174532925199433]],\n        ID[\"EPSG\",4171]],\n    CONVERSION[\"Lambert-93\",\n        METHOD[\"Lambert Conic Conformal (2SP)\",\n            ID[\"EPSG\",9802]],\n        PARAMETER[\"Latitude of false origin\",46.5,\n            ANGLEUNIT[\"degree\",0.0174532925199433],\n            ID[\"EPSG\",8821]],\n        PARAMETER[\"Longitude of false origin\",3,\n            ANGLEUNIT[\"degree\",0.0174532925199433],\n            ID[\"EPSG\",8822]],\n        PARAMETER[\"Latitude of 1st standard parallel\",49,\n            ANGLEUNIT[\"degree\",0.0174532925199433],\n            ID[\"EPSG\",8823]],\n        PARAMETER[\"Latitude of 2nd standard parallel\",44,\n            ANGLEUNIT[\"degree\",0.0174532925199433],\n            ID[\"EPSG\",8824]],\n        PARAMETER[\"Easting at false origin\",700000,\n            LENGTHUNIT[\"metre\",1],\n            ID[\"EPSG\",8826]],\n        PARAMETER[\"Northing at false origin\",6600000,\n            LENGTHUNIT[\"metre\",1],\n            ID[\"EPSG\",8827]]],\n    CS[Cartesian,2],\n        AXIS[\"easting (X)\",east,\n            ORDER[1],\n            LENGTHUNIT[\"metre\",1]],\n        AXIS[\"northing (Y)\",north,\n            ORDER[2],\n            LENGTHUNIT[\"metre\",1]],\n    USAGE[\n        SCOPE[\"unknown\"],\n        AREA[\"France\"],\n        BBOX[41.15,-9.86,51.56,10.38]],\n    ID[\"EPSG\",2154]]"), class = "crs"), n_empty = 0L)), row.names = c(NA, 
-5L), class = c("sf", "data.frame"), sf_column = "geometry", agr = structure(c(density = NA_integer_), class = "factor", .Label = c("constant", 
"aggregate", "identity")))
    
  exp_2 <- structure(list(density = c(2.35446082022629, 2.3832927533325, 
2.39117051553099, 2.37776579546915, 2.34373415502516), geometry = structure(list(
    structure(list(structure(c(462199.599999965, 462199.599999965, 
    463199.599999965, 463199.599999965, 462199.599999965, 6915158.74575047, 
    6916158.74575047, 6916158.74575047, 6915158.74575047, 6915158.74575047
    ), .Dim = c(5L, 2L))), class = c("XY", "POLYGON", "sfg")), 
    structure(list(structure(c(463199.599999965, 463199.599999965, 
    464199.599999965, 464199.599999965, 463199.599999965, 6915158.74575047, 
    6916158.74575047, 6916158.74575047, 6915158.74575047, 6915158.74575047
    ), .Dim = c(5L, 2L))), class = c("XY", "POLYGON", "sfg")), 
    structure(list(structure(c(464199.599999965, 464199.599999965, 
    465199.599999965, 465199.599999965, 464199.599999965, 6915158.74575047, 
    6916158.74575047, 6916158.74575047, 6915158.74575047, 6915158.74575047
    ), .Dim = c(5L, 2L))), class = c("XY", "POLYGON", "sfg")), 
    structure(list(structure(c(465199.599999965, 465199.599999965, 
    466199.599999965, 466199.599999965, 465199.599999965, 6915158.74575047, 
    6916158.74575047, 6916158.74575047, 6915158.74575047, 6915158.74575047
    ), .Dim = c(5L, 2L))), class = c("XY", "POLYGON", "sfg")), 
    structure(list(structure(c(466199.599999965, 466199.599999965, 
    467199.599999965, 467199.599999965, 466199.599999965, 6915158.74575047, 
    6916158.74575047, 6916158.74575047, 6915158.74575047, 6915158.74575047
    ), .Dim = c(5L, 2L))), class = c("XY", "POLYGON", "sfg"))), class = c("sfc_POLYGON", 
"sfc"), precision = 0, bbox = structure(c(xmin = 462199.599999965, 
ymin = 6915158.74575047, xmax = 467199.599999965, ymax = 6916158.74575047
), class = "bbox"), crs = structure(list(input = "EPSG:2154", 
    wkt = "PROJCRS[\"RGF93 / Lambert-93\",\n    BASEGEOGCRS[\"RGF93\",\n        DATUM[\"Reseau Geodesique Francais 1993\",\n            ELLIPSOID[\"GRS 1980\",6378137,298.257222101,\n                LENGTHUNIT[\"metre\",1]]],\n        PRIMEM[\"Greenwich\",0,\n            ANGLEUNIT[\"degree\",0.0174532925199433]],\n        ID[\"EPSG\",4171]],\n    CONVERSION[\"Lambert-93\",\n        METHOD[\"Lambert Conic Conformal (2SP)\",\n            ID[\"EPSG\",9802]],\n        PARAMETER[\"Latitude of false origin\",46.5,\n            ANGLEUNIT[\"degree\",0.0174532925199433],\n            ID[\"EPSG\",8821]],\n        PARAMETER[\"Longitude of false origin\",3,\n            ANGLEUNIT[\"degree\",0.0174532925199433],\n            ID[\"EPSG\",8822]],\n        PARAMETER[\"Latitude of 1st standard parallel\",49,\n            ANGLEUNIT[\"degree\",0.0174532925199433],\n            ID[\"EPSG\",8823]],\n        PARAMETER[\"Latitude of 2nd standard parallel\",44,\n            ANGLEUNIT[\"degree\",0.0174532925199433],\n            ID[\"EPSG\",8824]],\n        PARAMETER[\"Easting at false origin\",700000,\n            LENGTHUNIT[\"metre\",1],\n            ID[\"EPSG\",8826]],\n        PARAMETER[\"Northing at false origin\",6600000,\n            LENGTHUNIT[\"metre\",1],\n            ID[\"EPSG\",8827]]],\n    CS[Cartesian,2],\n        AXIS[\"easting (X)\",east,\n            ORDER[1],\n            LENGTHUNIT[\"metre\",1]],\n        AXIS[\"northing (Y)\",north,\n            ORDER[2],\n            LENGTHUNIT[\"metre\",1]],\n    USAGE[\n        SCOPE[\"unknown\"],\n        AREA[\"France\"],\n        BBOX[41.15,-9.86,51.56,10.38]],\n    ID[\"EPSG\",2154]]"), class = "crs"), n_empty = 0L)), row.names = c(NA, 
-5L), class = c("sf", "data.frame"), sf_column = "geometry", agr = structure(c(density = NA_integer_), class = "factor", .Label = c("constant", 
"aggregate", "identity")))
    
  exp_3 <- structure(list(density = c(1, 1, 1, 1, 1), geometry = structure(list(
    structure(list(structure(c(462199.599999965, 462199.599999965, 
    463199.599999965, 463199.599999965, 462199.599999965, 6915158.74575047, 
    6916158.74575047, 6916158.74575047, 6915158.74575047, 6915158.74575047
    ), .Dim = c(5L, 2L))), class = c("XY", "POLYGON", "sfg")), 
    structure(list(structure(c(463199.599999965, 463199.599999965, 
    464199.599999965, 464199.599999965, 463199.599999965, 6915158.74575047, 
    6916158.74575047, 6916158.74575047, 6915158.74575047, 6915158.74575047
    ), .Dim = c(5L, 2L))), class = c("XY", "POLYGON", "sfg")), 
    structure(list(structure(c(464199.599999965, 464199.599999965, 
    465199.599999965, 465199.599999965, 464199.599999965, 6915158.74575047, 
    6916158.74575047, 6916158.74575047, 6915158.74575047, 6915158.74575047
    ), .Dim = c(5L, 2L))), class = c("XY", "POLYGON", "sfg")), 
    structure(list(structure(c(465199.599999965, 465199.599999965, 
    466199.599999965, 466199.599999965, 465199.599999965, 6915158.74575047, 
    6916158.74575047, 6916158.74575047, 6915158.74575047, 6915158.74575047
    ), .Dim = c(5L, 2L))), class = c("XY", "POLYGON", "sfg")), 
    structure(list(structure(c(466199.599999965, 466199.599999965, 
    467199.599999965, 467199.599999965, 466199.599999965, 6915158.74575047, 
    6916158.74575047, 6916158.74575047, 6915158.74575047, 6915158.74575047
    ), .Dim = c(5L, 2L))), class = c("XY", "POLYGON", "sfg"))), class = c("sfc_POLYGON", 
"sfc"), precision = 0, bbox = structure(c(xmin = 462199.599999965, 
ymin = 6915158.74575047, xmax = 467199.599999965, ymax = 6916158.74575047
), class = "bbox"), crs = structure(list(input = "EPSG:2154", 
    wkt = "PROJCRS[\"RGF93 / Lambert-93\",\n    BASEGEOGCRS[\"RGF93\",\n        DATUM[\"Reseau Geodesique Francais 1993\",\n            ELLIPSOID[\"GRS 1980\",6378137,298.257222101,\n                LENGTHUNIT[\"metre\",1]]],\n        PRIMEM[\"Greenwich\",0,\n            ANGLEUNIT[\"degree\",0.0174532925199433]],\n        ID[\"EPSG\",4171]],\n    CONVERSION[\"Lambert-93\",\n        METHOD[\"Lambert Conic Conformal (2SP)\",\n            ID[\"EPSG\",9802]],\n        PARAMETER[\"Latitude of false origin\",46.5,\n            ANGLEUNIT[\"degree\",0.0174532925199433],\n            ID[\"EPSG\",8821]],\n        PARAMETER[\"Longitude of false origin\",3,\n            ANGLEUNIT[\"degree\",0.0174532925199433],\n            ID[\"EPSG\",8822]],\n        PARAMETER[\"Latitude of 1st standard parallel\",49,\n            ANGLEUNIT[\"degree\",0.0174532925199433],\n            ID[\"EPSG\",8823]],\n        PARAMETER[\"Latitude of 2nd standard parallel\",44,\n            ANGLEUNIT[\"degree\",0.0174532925199433],\n            ID[\"EPSG\",8824]],\n        PARAMETER[\"Easting at false origin\",700000,\n            LENGTHUNIT[\"metre\",1],\n            ID[\"EPSG\",8826]],\n        PARAMETER[\"Northing at false origin\",6600000,\n            LENGTHUNIT[\"metre\",1],\n            ID[\"EPSG\",8827]]],\n    CS[Cartesian,2],\n        AXIS[\"easting (X)\",east,\n            ORDER[1],\n            LENGTHUNIT[\"metre\",1]],\n        AXIS[\"northing (Y)\",north,\n            ORDER[2],\n            LENGTHUNIT[\"metre\",1]],\n    USAGE[\n        SCOPE[\"unknown\"],\n        AREA[\"France\"],\n        BBOX[41.15,-9.86,51.56,10.38]],\n    ID[\"EPSG\",2154]]"), class = "crs"), n_empty = 0L)), row.names = c(NA, 
-5L), class = c("sf", "data.frame"), sf_column = "geometry", agr = structure(c(density = NA_integer_), class = "factor", .Label = c("constant", 
"aggregate", "identity")))
    
expect_equal(object = test_1,
             expected = exp_1)

expect_equal(object = test_2,
             expected = exp_2)

expect_equal(object = test_3,
             expected = exp_3)

expect_is(test_1, "data.frame")
expect_is(test_2, "data.frame")
expect_is(test_3, "data.frame")

})

test_that("test erreur simulate_density", {
  
  data("shape_courseulles")
  
  
  expect_error(object = simulate_density(shape_obj = c(1,1,1),
                                           density_type = "uniform"))
  
  expect_error(object = simulate_density(shape_obj = shape_courseulles,
                                          density_type = "aleatoire"))
  
  expect_error(object = simulate_density(shape_obj = shape_courseulles,
                                           density_type = "gradient",
                                           gradient_direction = "SSE",
                                           wavelength = 40000,
                                           amplitude = 15))
  
  expect_error(object = simulate_density(shape_obj = shape_courseulles,
                                           density_type = "gradient",
                                           gradient_direction = "SE",
                                           amplitude = 15))
  
  expect_error(object = simulate_density(shape_obj = shape_courseulles,
                                           gradient_direction = "NE",
                                           density_type = "gradient",
                                           wavelength = "ohoh",
                                           amplitude = 15))
  
  expect_error(object = simulate_density(shape_obj = shape_courseulles,
                                           density_type = "random",
                                           wavelength = 40000,
                                           amplitude = 15))
  
  expect_error(object = simulate_density(shape_obj = shape_courseulles,
                                           density_type = "random",
                                           wavelength = 40000,
                                           amplitude = 15,
                                           nb_hotspots = "haha"))
  
  
})
```

## Simulate individuals

The `simulate_ind` function allows to simulate an approximate number of individuals/groups with an inhomogenous Poisson point process according to the densities provided.

From a sf dataframe containing density map `map_obj`, an inohomogene Poisson point process is used to simulate the presence of `N` individuals/groups on the map. The probability of presence of an individual/group is dependent on the density given by the map. Groups are simulated using a Poisson distribution, with parameter `mean_group_size`.  

The output is the simulated individuals in a dataframe. The dataframe contains three columns:        
-`x` : longitude of the simulated individual/group.     
-`y` : latitude of the simulated individual/group.     
- `size` : the number of individuals simulated on the location.

```{r function-simulate_ind}

#' Simulate individuals
#'
#' @description
#' `simulate_ind` allows to simulate a approximate number of individuals with a inhomogenous Poisson point process according to the densities provided.
#'
#' @details
#' This function need a grid sf object with density assosciated to each square of the grid.
#' For each simulated individuals, a size is associated. Thus, it is possible to simulate group. Group are simulated using a Poisson distribution, with parameter `mean_group_size`. By default size is 1.
#'
#' @param map_obj sf dataframe. Sf map with a colum containg density informations
#' @param N numeric. The number of individuals desired in the area.
#' @param mean_group_size numeric. Mean size of groups to simulate. By default = 1.
#' @param crs numeric. Projection system. By default: 2154. 
#'
#' @importFrom glue glue
#' @importFrom assertthat assert_that
#' @importFrom stats rpois
#' @importFrom dplyr mutate select filter
#' @importFrom sf st_centroid st_coordinates st_crs st_area
#' @importFrom sp coordinates<- proj4string<- gridded<- CRS
#' @importFrom maptools as.im.SpatialGridDataFrame
#'
#' @return The simulated individuals in a dataframe. The dataframe contains three columns, `x` longitude of the simulated individual, `y` latitude of the simulated individual and `size` the number of individuals simulated on the location (the possibility of simulate groupe will comming).  
#' @export

simulate_ind <- function(map_obj, N, mean_group_size = 1, crs = 2154) {
  
  # Function checks
  assert_that(inherits(map_obj, "sf"))
  if (!all(c("density") %in% names(map_obj))) {stop("map_obj must contain `density` column. Verify your column names.")}
  assert_that(is.numeric(map_obj$density))
  assert_that(is.numeric(crs))
  assert_that(is.numeric(N))
  assert_that(is.numeric(mean_group_size))

  
  map_obj <- map_obj %>%
    mutate(area = st_area(.))
  
  # Function 
  total_area <- sum(map_obj$area)
  average_density <- N / total_area
  
  map_obj <- map_obj %>%
    mutate(density = average_density * density / mean(density, na.rm = TRUE))
  
  # Create grid
  grid <- map_obj %>%
    st_centroid() %>%
    mutate(X = st_coordinates(.)[,1],
           Y = st_coordinates(.)[,2]) %>%
    as.data.frame() %>%
    select("X","Y","density")
  
  
  # Convert in grid class
  coordinates(grid) <- ~ X + Y
  proj4string(grid) <- CRS(st_crs(crs)$proj4string)
  gridded(grid) <- TRUE
  X_grid <- maptools::as.im.SpatialGridDataFrame(grid)
  
  # Inhomogenous Poisson point process
  ppp <- spatstat.core::rpoispp(lambda = X_grid, drop = TRUE)
  sim_ind <- data.frame(x = ppp$x, y = ppp$y)
  
  # Possibility to add group size
  sim_ind <- sim_ind %>%
    mutate(size = rpois(nrow(sim_ind), lambda = (mean_group_size - 1)) + 1)
  
  return(sim_ind)
}

```

### Examples

For these examples, we used `shape_courseulles`, a dataframe included in this package and the function `simulate_density` to simulate a density map. Then, with used `simulate_ind` to simulate individuals:          
- (1) simulation of **200 individuals** in the area.     
- (2) simulation of **100 groups** with a **mean group size of 5 individuals**.       

The function returns a dataframe, containing the different individuals simulated in line, the size of each group and their geographic coordinates in column. 

```{r examples-simulate_ind, warning = FALSE, fig.height = 3, fig.width= 7}

library(ggplot2)
data("shape_courseulles")

# First, create a map with a gradient density from the North
map <- simulate_density(shape_obj = shape_courseulles,
                              grid_size = 1000,
                              density_type = "gradient",
                              gradient_direction = "N",
                              wavelength = 20000,
                              amplitude = 15)

# ------------------------------
# Example 1. Simulate the presence of 200 individuals 
# ------------------------------

ind <- simulate_ind(map_obj = map, N = 200)

# Plot
ggplot() +
  geom_sf(data = map, aes(fill = density)) +
  geom_point(data = ind, aes(x = x, y = y)) +
  theme(panel.background = element_rect(fill = "white"),
        panel.grid.major = element_line(colour = "#EDEDE9"))


# ------------------------------
# Example 2. Simulate the presence of 100 groups with a mean group size of 5 individuals 
# ------------------------------

ind <- simulate_ind(map_obj = map, mean_group_size = 5, N = 100)

# Plot
ggplot() +
  geom_sf(data = map) +
  geom_point(data = ind, aes(x = x, y = y, color = size)) +
  theme(panel.background = element_rect(fill = "white"),
        panel.grid.major = element_line(colour = "#EDEDE9"))
  
```

```{r tests-simulate_ind}
library(testthat)
library(dplyr)

test_that("simulate_ind works", {
  expect_true(inherits(simulate_ind, "function")) 
})

test_that("test conformite simulate_ind", {
  
  data("shape_courseulles")
  
  set.seed(2022)
  
  # First, create a density map
  map <- simulate_density(shape_obj = shape_courseulles,
                            density_type = "gradient",
                            gradient_direction = "N",
                            wavelength = 20000,
                            amplitude = 500)
  
  test_1 <- simulate_ind(map_obj = map, N = 500) %>%
                 slice(1:5)
  
  test_2 <- simulate_ind(map_obj = map, N = 500, mean_group_size = 3) %>%
                 slice(1:5)

exp_1 <- structure(list(x = c(442098.238355977, 420533.286240681, 443527.738948383, 
411815.477216414, 470612.945042581), y = c(6926762.23628262, 
6944532.6011364, 6939771.26691599, 6944138.62147687, 6945281.02163264
), size = c(1, 1, 1, 1, 1)), class = "data.frame", row.names = c(NA, 
-5L))

exp_2 <- structure(list(x = c(472685.185622455, 438778.109058536, 437555.810525346, 
459633.647628858, 456106.671207615), y = c(6940978.15048733, 
6932096.386525, 6941737.78689435, 6950947.10736784, 6928151.73028891
), size = c(3, 5, 7, 3, 4)), class = "data.frame", row.names = c(NA, 
-5L))

  expect_equal(object = test_1,
               expected = exp_1)
  
  expect_equal(object = test_2,
               expected = exp_2)

  expect_is(test_1, "data.frame")
  expect_is(test_2, "data.frame")

})

test_that("test erreur simulate ind", {
  
  data(iris)
  
  expect_error(object = simulate_ind(map_obj = iris, N = 500))
  
  # First, create a density map
  map <- simulate_density(shape_obj = shape_courseulles,
                            density_type = "gradient",
                            gradient_direction = "N",
                            wavelength = 20000,
                            amplitude = 500)
  
  expect_error(object = simulate_ind(map_obj = map, N = "haha"))
  expect_error(object = simulate_ind(map_obj = map))

  
  map_test <- map %>%
    rename(nop = density)
  
  expect_error(object = simulate_ind(map_obj = map_test,N = 500))
  
  map_test <- map
  map_test$density[5] <- "nop"
  
  expect_error(object = simulate_ind(map_obj = map_test, N = 500))
    expect_error(object = simulate_ind(map_obj = map, N = 500, mean_group_size = "ahah"))

  expect_error(object = simulate_ind(map_obj = map,
                                     N = 500,
                                     crs = "nop"))
  
})

```


```{r development-inflate, eval=FALSE}
# Run but keep eval=FALSE to avoid infinite loop
# Execute in the console gradient_directionectly
fusen::inflate(flat_file = "dev/flat_population_abundance_emulator.Rmd", 
               vignette_name = "Population Abundance Emulator",
               open_vignette = FALSE,
               check = FALSE,
               overwrite = TRUE)
```
