---
title: "flat_minimal.Rmd empty"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r development, include=FALSE}
library(testthat)
```


## Simulate Observation
`simulate_obs` allows to simulate dataset of observations according to:
- The individuals simulated on the density map
- The transect design simulated
- A detection probability     

To determine the detection probability it is possible to choose:
- The form of the detection function : **uniform** or **half-normal**
- The maximum distance of observation (**truncation**)
- The probability of observation at distance 0 (**g_zero**)
- The effective strip width (**esw**) for half-normal detection function

The output is a dataframe containing all the individuals/groups of the map. The dataframe contains four columns:         
- `object_ID` : unique identification of individuals/groups 
- `size` : size of group (=1 for individuals).    
- `detected` : 0 for non detected or 1 for detected individuals/groups
- `proba` : probability of detection of the individual/group (according to the distance to the nearest transect/segment)
- `distance` : distance in m between individual/group and the nearest transect/segment.
- `seg_ID` : identification of the nearest segment/transect
- `x` : longitude of the individual/group
- `y` : latitude of the individual/ group

```{r function-simulate_obs}

#' Simulate observation
#'
#' @description
#' `simulate_obs` allows to simulate to simulate dataset of observations according to individuals simulated on the density map, a transect design a detection probability 
#
#' @details
#' To calculate the detection probability, the function calculate first the distance between the individual/group and the nearest transect.
#'
#' @param ind_obj dataframe. Individuals simulated with their coordinates.
#' @param transect_obj sf dataframe. Transect/segments data.
#' @param key character. Form of the detection function "hn" or "unif".
#' @param esw numeric. Effective strip width in m. This argument is needed only for the 'hn' form.
#' @param g_zero numeric. The detection probability at distance 0. By default 1.
#' @param truncation numeric. A single numeric value in m describing the longest distance at which an object may be observed. By default = NA.
#' @param crs numeric. Projection system. By default = 2154.
#'
#' @importFrom dplyr mutate rename n
#' @importFrom stats rbinom
#' @importFrom units drop_units
#' @importFrom sf st_as_sf st_nearest_feature st_distance st_drop_geometry
#' @importFrom assertthat assert_that
#'
#' @return dataframe. The dataframe contains all the individuals/groups of the map. The dataframe contains the identification of individuals/groups, their size, if their are detected, their probability of detection, the identification of nearest transect/segment and their localisation. 
#' @export


simulate_obs <- function(ind_obj, transect_obj, key, esw = NA, g_zero = 1, truncation = NA, crs = 2154) {
  
  # Function checks
  
   assert_that(inherits(ind_obj, "data.frame"))
  if (!all(c("x", "y") %in% names(ind_obj))) {stop("ind_obj must contain `x` and `y` coordinates columns. Verify your column names.")}
  assert_that(is.numeric(g_zero))
  assert_that(inherits(transect_obj, "sf"))
  assert_that(is.numeric(crs))
  if(!(key %in% c("unif", "hn"))){stop("Key argument must be `unif` or `hn`.")}
  
  # Function
  
  # Calculate distance between individuals and nearest transect/segment
  
  # obs point in sf format
  dsf <- ind_obj %>%
    select("x","y") %>%
    st_as_sf(coords = c("x","y"), crs = crs)
  
  # Calculate the closest transect/segment
  nearest_spee <- st_nearest_feature(x = dsf, y = transect_obj)
  
  # Calculate distance between point and transect
  dist_obj <- st_distance(dsf, transect_obj[nearest_spee,], by_element = TRUE)
  
  transect_obj <- transect_obj %>%
    st_drop_geometry()
  
  # summary table
  dist_obj <- dist_obj %>%
    as.data.frame() %>%
    rename(distance = '.') %>%
    mutate(seg_ID = transect_obj[nearest_spee,'seg_ID'],
           size = ind_obj$size,
           distance_km = distance / 1e3,
           x = ind_obj$x,
           y = ind_obj$y,
           object_ID = 1:n()) %>%
    drop_units()
  
  if(key == 'hn'){
    
    if(is.numeric(esw)==FALSE) {stop("With 'hn' key, esw must have a numeric value")}
    
    esw_km <- esw / 1000
    sigma <- scale_hn(esw = esw_km)
    dist_obj <- dist_obj %>%
      mutate(proba = exp(-(distance_km)^2 / (2 * sigma * sigma))*g_zero) %>%
      mutate(detected = rbinom(nrow(dist_obj), size = 1, prob = proba))
    
    if(is.na(truncation) == FALSE){
      dist_obj$detected[dist_obj$distance > truncation] <- 0
    }
    
  }
  
  if(key == 'unif'){
    
    if(is.numeric(truncation)==FALSE) {stop("With 'unif' key, truncation must have a numeric value")}

    dist_obj <- dist_obj %>%
      mutate(proba = g_zero) %>%
      mutate(detected = rbinom(nrow(dist_obj), size = 1, prob = proba))
    
    dist_obj$detected[dist_obj$distance > truncation] <- 0
    dist_obj$proba[dist_obj$distance > truncation] <- 0
  }
  
  
  dist_obj <- dist_obj %>%
    select(object_ID, size, detected, proba, distance, seg_ID, x, y)
  
  return(dist_obj)
  
}
```

### Examples

For this example, `shape_courseulles`, a dataframe included in this package is used. With `simulate_obs` observations of individuals and group are simulated under diffrent conditions:     
- (1) **Half normal** detection probability equal to **1** at 0 distance (g_zero) with a effective half width of **180m** (esw). 
- (2) **Uniform** detection probability equal to **1** below distance **200m** (truncation).    

```{r examples-simulate_obs, warning = FALSE}

library(ggplot2)
data("shape_courseulles")

# First, create a density map
map <- simulate_density(shape_obj = shape_courseulles,
                        density_type = "gradient",
                        gradient_direction = "N",
                        wavelength = 20000,
                        amplitude = 500)

# Then simulate the presence of individuals in the study area 
ind <- simulate_ind(map_obj = map, N = 500)

# Then create transects
transects <- simulate_transects(shape_obj = map,
                                design = "systematic",
                                line.length = 400000,
                                design.angle = 2,
                                segmentize = TRUE,
                                length_segs = 2000)

# Finally, detection of individuals simulated on the map 
# according to simulated densities and simulated transects :

# ------------------------------
# Example 1 : With a half normal detection probability equal to 1 at 0 distance (g_zero)
# with a effective half width of 180 m.
# ------------------------------

obs <- simulate_obs(ind_obj = ind,
                    transect_obj = transects,
                    key = "hn",
                    g_zero = 1,
                    esw = 180)

# Plot detection probability
ggplot(obs, aes(x=distance, y=proba)) +
  geom_point(color = "#EE6C4D") +
  xlim(0,500) 

# Plot on map
ggplot() +
  geom_sf(data = map, fill = "#CDDAFD", color = "#CDDAFD") +
  geom_sf(data = transects, color = "black") +
  geom_point(data=obs[obs$detected==0,], aes(x=x, y=y), shape=20, color="#051923") +
  geom_point(data=obs[obs$detected==1,], aes(x=x, y=y), shape=21, fill="#EE6C4D") +
  labs(caption = paste("Sightings = ", sum(obs$detected), sep = " ")) +
  theme(legend.position = "none",
        panel.background = element_rect(fill = "white"),
        panel.grid.major = element_line(colour = "#EDEDE9"))


# ------------------------------
# Example 2 : With a uniforme detection probability equal to 1 below distance 200 m.
# ------------------------------

obs <- simulate_obs(ind_obj = ind,
                    transect_obj = transects,
                    key = "unif",
                    g_zero = 1,
                    truncation = 200)

# Plot detection probability
ggplot(obs, aes(x=distance, y=proba)) +
  geom_point(color = "#EE6C4D") +
  xlim(0,500) 

# Plot on map
ggplot() +
  geom_sf(data = map, fill = "#CDDAFD", color = "#CDDAFD") +
  geom_sf(data = transects, color = "black") +
  geom_point(data=obs[obs$detected==0,], aes(x=x, y=y), shape=20, color="#051923") +
  geom_point(data=obs[obs$detected==1,], aes(x=x, y=y), shape=21, fill="#EE6C4D") +
  labs(caption = paste("Sightings = ", sum(obs$detected), sep = " ")) +
  theme(legend.position = "none",
        panel.background = element_rect(fill = "white"),
        panel.grid.major = element_line(colour = "#EDEDE9"))

```

```{r tests-simulate_obs}
library(testthat)
library(dplyr)


test_that("simulate_obs works", {
  expect_true(inherits(simulate_obs, "function")) 
})


test_that("test conformite simulate_obs", {
  
  data("shape_courseulles")
  
  set.seed(2022)
  
  # First, create a density map
  map <- simulate_density(shape_obj = shape_courseulles,
                            density_type = "gradient",
                            gradient_direction = "N",
                            wavelength = 20000,
                            amplitude = 500)
  # Simulate ind
  ind <- simulate_ind(map_obj = map, N = 500)
  
  # Then create transects
  transects <- simulate_transects(shape_obj = map,
                               design = "systematic",
                               line.length = 400000,
                               design.angle = 2,
                               segmentize = TRUE,
                               length_segs = 2000)
  
  
  
  test_1 <- simulate_obs(ind_obj = ind,
                      transect_obj = transects,
                      key = "hn",
                      g_zero = 1,
                      esw = 180) %>%
    slice(1:5)
  
  
  test_2 <- simulate_obs(ind_obj = ind,
                       transect_obj = transects,
                       key = "unif",
                       g_zero = 1,
                       truncation = 200) %>%
    slice(1:5)
  
  test_3 <- simulate_obs(ind_obj = ind,
                       transect_obj = transects,
                       key = "hn",
                       g_zero = 0.8,
                       esw = 180) %>%
    slice(1:5)
  
  
  test_4 <- simulate_obs(ind_obj = ind,
                       transect_obj = transects,
                       key = "unif",
                       g_zero = 0.6,
                       truncation = 300) %>%
    slice(1:5)
  
  
  exp_1 <- structure(list(object_ID = 1:5, size = c(1, 1, 1, 1, 1), detected = c(0L, 
0L, 1L, 0L, 0L), proba = c(5.57408603285241e-08, 4.66293367408908e-19, 
0.602629418799049, 1.00932158605189e-82, 2.70796644221945e-38
), distance = c(830.078156629012, 1319.57027537831, 144.543000948544, 
2790.81895410615, 1889.03814715369), seg_ID = c("8-3", "5-10", 
"8-9", "4-8", "12-16"), x = c(442098.238355977, 420533.286240681, 
443527.738948383, 411815.477216414, 470612.945042581), y = c(6926762.23628262, 
6944532.6011364, 6939771.26691599, 6944138.62147687, 6945281.02163264
)), row.names = c(NA, -5L), class = "data.frame")
    
  exp_2 <- structure(list(object_ID = 1:5, size = c(1, 1, 1, 1, 1), detected = c(0, 
0, 1, 0, 0), proba = c(0, 0, 1, 0, 0), distance = c(830.078156629012, 
1319.57027537831, 144.543000948544, 2790.81895410615, 1889.03814715369
), seg_ID = c("8-3", "5-10", "8-9", "4-8", "12-16"), x = c(442098.238355977, 
420533.286240681, 443527.738948383, 411815.477216414, 470612.945042581
), y = c(6926762.23628262, 6944532.6011364, 6939771.26691599, 
6944138.62147687, 6945281.02163264)), row.names = c(NA, -5L), class = "data.frame")
    
  exp_3 <- structure(list(object_ID = 1:5, size = c(1, 1, 1, 1, 1), detected = c(0L, 
0L, 1L, 0L, 0L), proba = c(4.45926882628192e-08, 3.73034693927126e-19, 
0.482103535039239, 8.0745726884151e-83, 2.16637315377556e-38), 
    distance = c(830.078156629012, 1319.57027537831, 144.543000948544, 
    2790.81895410615, 1889.03814715369), seg_ID = c("8-3", "5-10", 
    "8-9", "4-8", "12-16"), x = c(442098.238355977, 420533.286240681, 
    443527.738948383, 411815.477216414, 470612.945042581), y = c(6926762.23628262, 
    6944532.6011364, 6939771.26691599, 6944138.62147687, 6945281.02163264
    )), row.names = c(NA, -5L), class = "data.frame")
    
  exp_4 <- structure(list(object_ID = 1:5, size = c(1, 1, 1, 1, 1), detected = c(0, 
0, 0, 0, 0), proba = c(0, 0, 0.6, 0, 0), distance = c(830.078156629012, 
1319.57027537831, 144.543000948544, 2790.81895410615, 1889.03814715369
), seg_ID = c("8-3", "5-10", "8-9", "4-8", "12-16"), x = c(442098.238355977, 
420533.286240681, 443527.738948383, 411815.477216414, 470612.945042581
), y = c(6926762.23628262, 6944532.6011364, 6939771.26691599, 
6944138.62147687, 6945281.02163264)), row.names = c(NA, -5L), class = "data.frame")
    
    
expect_equal(object = test_1,
             expected = exp_1)

expect_equal(object = test_2,
             expected = exp_2)

expect_equal(object = test_3,
             expected = exp_3)

expect_equal(object = test_4,
             expected = exp_4)

expect_is(test_1, "data.frame")
expect_is(test_2, "data.frame")
expect_is(test_3, "data.frame")
expect_is(test_4, "data.frame")

})

test_that("test erreur simulate_obs", {
  


  expect_error(object = simulate_obs(ind_obj = c(1,1,2),
                       transect_obj = transects,
                       key = "hn",
                       g_zero = 1,
                       esw = 180))
  
  expect_error(object = simulate_obs(ind_obj = ind,
                       transect_obj = c(1,1,2),
                       key = "hn",
                       g_zero = 1,
                       esw = 180))
  
  expect_error(object = simulate_obs(ind_obj = ind,
                       transect_obj = transects,
                       key = "hn",
                       esw = '180'))
  
  expect_error(object = simulate_obs(ind_obj = ind,
                       transect_obj = transects,
                       key = "unif",
                       g_zero = 1,
                       truncation = '180'))
  
})
```

```{r function-esw_hn}

#' esw_hn
#'
#' @param sigma numeric. Sigma of half normal function.
#'
#' @importFrom stats pnorm dnorm
#' @importFrom assertthat assert_that
#'
#' @return numeric. esw value associated to the sigma given.
#' @keywords internal
#' @export

esw_hn <- function(sigma){
  
  assert_that(is.numeric(sigma))
  
  esw <- (pnorm(+Inf, 0, sigma) - 0.5) / dnorm(0, 0, sigma)
  return(esw)
  
  }

```

```{r tests-scale_hn}
library(testthat)

test_that("scale_hn works", {
  expect_true(inherits(scale_hn, "function")) 
})


test_that("test conformite scale_hn", {
  
  expect_equal(round(scale_hn(esw = 0.16), digits=3),
               expected = 0.128)
  
  expect_is(scale_hn(esw = 0.16), "numeric")
  
})

test_that("test erreur scale_hn", {
  
  expect_error(object = scale_hn(esw = "haha"))
  
})
```

```{r function-scale_hn}

#' Scale hn
#'
#' @param esw numeric. Effective strip width.
#' @param lower numeric. Lower range of search.
#' @param upper numeric. Upper range of search.
#'
#' @importFrom stats uniroot
#' @importFrom assertthat assert_that
#'
#' @return numeric. The sigma parameter of a half normal function associated with a esw value.
#' @keywords internal
#' @export


scale_hn <- function(esw, lower = 1e-3, upper = 5) {
  
  assert_that(is.numeric(esw))
  res <- as.numeric(uniroot(function(x, ...) {esw_hn(sigma = x) - esw},
                            lower = lower,
                            upper = upper,
                            tol = 1e-8)[1])
  return(res)
}

```

```{r tests-esw_hn}
library(testthat)

test_that("esw_hn works", {
  expect_true(inherits(esw_hn, "function")) 
})


test_that("test conformite esw_hn", {
  
  expect_equal(round(esw_hn(sigma = 0.3), digits = 3),
               expected = 0.376)
  
  expect_is(esw_hn(sigma = 0.3), "numeric")
  
})

test_that("test erreur esw_hn", {
  
  expect_error(object = esw_hn(sigma = "haha"))
  
})
```

```{r development-inflate, eval=FALSE}
# Run but keep eval=FALSE to avoid infinite loop
# Execute in the console gradient_directionectly
fusen::inflate(flat_file = "dev/flat_observation_data_emulator.Rmd", 
               vignette_name = "Observation Data Emulator",
               open_vignette = FALSE,
               check = FALSE,
               overwrite = TRUE)
```
